\documentclass{article}

% packages
\usepackage[a4paper, margin=2.4cm]{geometry}
\usepackage{multicol}

\begin{document}

    \begin{titlepage}
        \begin{center}
            \vspace*{2cm}

            {\huge \textbf{xCore-200 Cellular Automaton Farm}}

            \vspace{0.5cm}

            {\Large COMS20001 Concurrent Computing CW1}

            \vspace{0.5cm}

            {\large Team 6}

            \vspace{1cm}
            
            \hspace*{1cm} {\Large \textbf{Ruairi Fox}} \hfill {\Large \textbf{Liam Dalgarno}} \hspace*{1cm} \\~\\[-0.5em]
            \hspace*{1cm} MEng. Computer Science \hfill MEng. Computer Science  \hspace*{1cm} \\~\\[-1em]
            \hspace*{1cm} rf17160@bristol.ac.uk  \hfill ld17285@bristol.ac.uk  \hspace*{1cm} 

            \vspace{1cm}

            {\large \today}
        \end{center}
    \end{titlepage}

    \section{Functionality and Design}
    1 Page Max: Outline what functionality you have implemented, which problems you have solved with your implementation and how your program is designed to solve the problems efficiently and effectively
    \pagebreak

    \section{Tests and Experiments}
    (2 pages max): Show the result of the given 16x16 image after 2 rounds. Describe briefly the other experiments you carried out, provide a selection of appropri ate results and output images. This must be done for at least the example images provided and for at least one example image of your own choosing (showcasing the merit of your system). List the important factors responsible for virtues and limitations of your system. 
    \pagebreak

    \section{Critical Analysis}
    Critical Analysis (1 page max): Discuss the performance of your program with reference to the results obtained and indicate ways in which it might be improved. State clearly what maximal size of image your system can process and how fast your system can evolve the Game of Life. (Make sure your team’s names, course, and email addresses appears on page 1 of the report.) 
\end{document}